PANCHANGE_data_preprocessing

### 2020-08-07 PANCHANGE_data_preprocessing2020-07-15.Rmd
read in of coping ocir, phq, gad, and pcl

```{r glad phq cleaning}
glad.phq.raw.id <- glad.phq.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.glad = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    phq.little_interest_or_pleasure_in_doing_things_prepan = phq.little_interest_or_pleasure_in_doing_things,
    phq.feeling_down_depressed_or_hopeless_prepan = phq.feeling_down_depressed_or_hopeless,
    phq.staying_asleep_sleeping_trouble_prepan = phq.staying_asleep_sleeping_trouble,
    phq.feeling_tired_or_having_little_energy_prepan = phq.feeling_tired_or_having_little_energy,
    phq.poor_appetite_or_overeating_prepan = phq.poor_appetite_or_overeating,
    phq.feeling_bad_failure_family_prepan = phq.feeling_bad_failure_family,
    phq.trouble_concentrating_reading_newspaper_prepan = phq.trouble_concentrating_reading_newspaper,
    phq.moving_fidgety_noticed_opposite_prepan = phq.moving_fidgety_noticed_opposite,
    phq.dead_hurting_thoughts_prepan = phq.dead_hurting_thoughts
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

```{r coping glad gad cols}
coping.glad.gad.raw <- readRDS(file = paste0(data.raw_path,"/coping_glad/gad_coping_glad.rds"))
dim(coping.glad.gad.raw)
colnames(coping.glad.gad.raw)
```

@@

```{r coping glad gad cleaning}
coping.glad.gad.raw.id <- coping.glad.gad.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.glad = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    startDate.coping.glad = startDate,
    gad.feeling_nervous_anxious_or_on_edge_retro = gad7.feeling_nervous_anxious_or_on_edge,
    gad.control_worrying_stop_retro = gad7.control_worrying_stop,
    gad.worrying_too_much_about_different_things_retro = gad7.worrying_too_much_about_different_things,
    gad.trouble_relaxing_retro = gad7.trouble_relaxing,
    gad.sit_restless_hard_retro = gad7.sit_restless_hard,
    gad.becoming_easily_annoyed_or_irritable_retro = gad7.becoming_easily_annoyed_or_irritable,
    gad.awful_feeling_afraid_happen_retro = gad7.awful_feeling_afraid_happen,
    gad.feeling_nervous_anxious_or_on_edge_base = gad7.feeling_nervous_anxious_or_on_edge.1,
    gad.control_worrying_stop_base = gad7.control_worrying_stop.1,
    gad.worrying_too_much_about_different_things_base = gad7.worrying_too_much_about_different_things.1,
    gad.trouble_relaxing_base = gad7.trouble_relaxing.1,
    gad.sit_restless_hard_base = gad7.sit_restless_hard.1,
    gad.becoming_easily_annoyed_or_irritable_base = gad7.becoming_easily_annoyed_or_irritable.1,
    gad.awful_feeling_afraid_happen_base = gad7.awful_feeling_afraid_happen.1,
    gad.feeling_nervous_anxious_or_on_edge_retro_numeric = gad7.feeling_nervous_anxious_or_on_edge_numeric,
    gad.control_worrying_stop_retro_numeric = gad7.control_worrying_stop_numeric,
    gad.worrying_too_much_about_different_things_retro_numeric = gad7.worrying_too_much_about_different_things_numeric,
    gad.trouble_relaxing_retro_numeric = gad7.trouble_relaxing_numeric,
    gad.sit_restless_hard_retro_numeric = gad7.sit_restless_hard_numeric,
    gad.becoming_easily_annoyed_or_irritable_retro_numeric = gad7.becoming_easily_annoyed_or_irritable_numeric,
    gad.awful_feeling_afraid_happen_retro_numeric = gad7.awful_feeling_afraid_happen_numeric,
    gad.feeling_nervous_anxious_or_on_edge_base_numeric = gad7.feeling_nervous_anxious_or_on_edge.1_numeric,
    gad.control_worrying_stop_base_numeric = gad7.control_worrying_stop.1_numeric,
    gad.worrying_too_much_about_different_things_base_numeric = gad7.worrying_too_much_about_different_things.1_numeric,
    gad.trouble_relaxing_base_numeric = gad7.trouble_relaxing.1_numeric,
    gad.sit_restless_hard_base_numeric = gad7.sit_restless_hard.1_numeric,
    gad.becoming_easily_annoyed_or_irritable_base_numeric = gad7.becoming_easily_annoyed_or_irritable.1_numeric,
    gad.awful_feeling_afraid_happen_base_numeric = gad7.awful_feeling_afraid_happen.1_numeric
  ) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

```{r coping glad pcl cols}
coping.glad.pcl.raw <- readRDS(file = paste0(data.raw_path,"/coping_glad/pcl_coping_glad.rds"))
dim(coping.glad.pcl.raw)
colnames(coping.glad.pcl.raw)
```

@@

```{r coping glad phq cols}
coping.glad.phq.raw <- readRDS(file = paste0(data.raw_path, "/coping_glad/phq_coping_glad.rds"))
dim(coping.glad.phq.raw)
colnames(coping.glad.phq.raw)
```

>>>>

```{r glad phq cleaning}
glad.phq.raw.id <- glad.phq.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.glad = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    phq.problems_made_difficult_care, # Impairment
    phq.pandemic_felt_feelings, # Comparison to before the pandemic (retro)
    phq.little_interest_or_pleasure_in_doing_things_prepan = phq.little_interest_or_pleasure_in_doing_things,
    phq.feeling_down_depressed_or_hopeless_prepan = phq.feeling_down_depressed_or_hopeless,
    phq.staying_asleep_sleeping_trouble_prepan = phq.staying_asleep_sleeping_trouble,
    phq.feeling_tired_or_having_little_energy_prepan = phq.feeling_tired_or_having_little_energy,
    phq.poor_appetite_or_overeating_prepan = phq.poor_appetite_or_overeating,
    phq.feeling_bad_failure_family_prepan = phq.feeling_bad_failure_family,
    phq.trouble_concentrating_reading_newspaper_prepan = phq.trouble_concentrating_reading_newspaper,
    phq.moving_fidgety_noticed_opposite_prepan = phq.moving_fidgety_noticed_opposite,
    phq.dead_hurting_thoughts_prepan = phq.dead_hurting_thoughts
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

```{r coping glad gad cols}
coping.glad.gad.raw <- readRDS(file = paste0(data.raw_path,"/glad/gad_coping_glad.rds"))
dim(coping.glad.gad.raw)
colnames(coping.glad.gad.raw)
```

@@

```{r coping glad gad cleaning}
coping.glad.gad.raw.id <- coping.glad.gad.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.glad = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    startDate.coping.glad = startDate,
    gad.problems_made_difficult_care, # Impairment
    gad.pandemic_felt_feelings, # Comparison to before the pandemic (retro)
    gad.feeling_nervous_anxious_or_on_edge_retro = gad.feeling_nervous_anxious_or_on_edge,
    gad.control_worrying_stop_retro = gad.control_worrying_stop,
    gad.worrying_too_much_about_different_things_retro = gad.worrying_too_much_about_different_things,
    gad.trouble_relaxing_retro = gad.trouble_relaxing,
    gad.sit_restless_hard_retro = gad.sit_restless_hard,
    gad.becoming_easily_annoyed_or_irritable_retro = gad.becoming_easily_annoyed_or_irritable,
    gad.awful_feeling_afraid_happen_retro = gad.awful_feeling_afraid_happen,
    gad.feeling_nervous_anxious_or_on_edge_base = gad.feeling_nervous_anxious_or_on_edge.1,
    gad.control_worrying_stop_base = gad.control_worrying_stop.1,
    gad.worrying_too_much_about_different_things_base = gad.worrying_too_much_about_different_things.1,
    gad.trouble_relaxing_base = gad.trouble_relaxing.1,
    gad.sit_restless_hard_base = gad.sit_restless_hard.1,
    gad.becoming_easily_annoyed_or_irritable_base = gad.becoming_easily_annoyed_or_irritable.1,
    gad.awful_feeling_afraid_happen_base = gad.awful_feeling_afraid_happen.1
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

```{r coping glad pcl cols}
coping.glad.pcl.raw <- readRDS(file = paste0(data.raw_path,"/glad/pcl_coping_glad.rds"))
dim(coping.glad.pcl.raw)
colnames(coping.glad.pcl.raw)
```

@@

```{r coping glad phq cols}
coping.glad.phq.raw <- readRDS(file = paste0(data.raw_path, "/glad/phq_coping_glad.rds"))
dim(coping.glad.phq.raw)
colnames(coping.glad.phq.raw)
```
